Optimal (Multiway) Spatial Joins

### 2024-05-26 msj.tex
yufei

        \item $\sum_{\bm{t}} |\dcross_H(\bm{t})| \le \out$ and $\sum_{\bm{t}} |\dcross_V(\bm{t})| \le \out$.
    }
\end{lemma}

@@

        \item $\sum_{\bm{t}} |\contained_{R_{k-2}}(\bm{t})| \le \out$.
    }
\end{lemma}

>>>>

        \item $\sum_{\bm{t}} |\dcross_H(\bm{t})| \le \out$ and $\sum_{\bm{t}} |\dcross_V(\bm{t})| \le \out$, where the two summations are over all $\bm{t} \in \J(R_1', R'_2, ..., R'_{k-2})$.
    }
\end{lemma}

@@

        \item $\sum_{\bm{t}} |\contained_{R_{k-2}}(\bm{t})| \le \out$, where the summation is over all $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$.
    }
\end{lemma}
